Article 2 : Antioxidants may encourage the spread of lung cancer rather than prevent it

### 2019-11-01 _posts/2019-10-18-article-2/article-2.Rmd
correction faute

---
title: "Article 2 : Antioxidants may encourage the spread of lung cancer rather than prevent it"
author:
  - name: Aurélie Pinchart
date: 11-01-2019
categories:
  - antioxidants
  - oxidatice stress
preview: article-2_image/antioxidants.jpg
output:
  distill::distill_article:
    self_contained: false
---

>>>>

---
title: "Article 2 : Antioxidants may encourage the spread of lung cancer rather than prevent it"
author:
  - name: Aurélie Pinchart
date: 11-01-2019
categories:
  - antioxidants
  - oxidative stress
preview: article-2_image/antioxidants.jpg
output:
  distill::distill_article:
    self_contained: false
---
